---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

This file is a combination of notes from lecture and my code for plots on my flexdashboard. Still, I am housing it in this project/repo since it was used to create my website, but this page itself will not be displayed online. Instead, I will use this code in the dashboard.rmd to build that page.

## Load packages and data

```{r}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

Let's get some data.

```{r}
data("instacart")

instacart = 
  instacart %>% 
  as_tibble(instacart)
```

Let's make a line plot with plotly!

```{r}
instacart %>%
  group_by(order_dow, department) %>% 
  summarise(orders = n()) %>%
  ungroup() %>%
  plot_ly(
    x = ~order_dow, y = ~orders, color = ~department,
    type = "scatter", mode = "lines+markers", colors = "viridis") %>%
  layout(title = 'Number of products by day', xaxis = list(title = 'Day of the week'))
```

Here's a scatterplot:

```{r}
instacart %>% 
  count(aisle) %>%
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  plot_ly(
    x = ~aisle, y = ~n,
    type = "scatter", mode = "markers") %>%
  layout(title = 'Number of items ordered in each aisle', xaxis = list(title = 'Aisle'), colors = "viridis")
```

Now onto boxplots!

```{r}
instacart %>%
  plot_ly(
    y = ~order_hour_of_day, color = ~department,
    type = "box", colors = "viridis") %>%
    layout(title = 'Hour of order by department', xaxis = list(title = 'Department'), yaxis = list(title = 'Order hour of day'))
```

Finally, let's make a bar graph.
 
```{r}
instacart %>% 
  count(department) %>% 
  mutate(department = fct_reorder(department, n)) %>% 
  plot_ly(
  x = ~department, y = ~n, color = ~department,
  type = "bar", colors = "viridis") %>%
  layout(title = 'Number of items ordered in each department')
```

## Create a dashboard

Not here though. Dashboards are their own page (see: dashboard.rmd)
